### 2021-07-20 doc/thesis/chapters/system-design-process.tex
new diagrams

Two commonly used languages therefor are VHDL and Verilog.
Both have similar features to describe hardware in the signal level, with parallel structures and timing-dependent architectures.
The languages can describe a design in a hierarchical order, so that the separate modules can be constructed in a way that an overview of the functionality of the system remains given.
Synthesis, as well as simulation is supported, which allows efficient development of RTL designs.\\

@@

Fig. \ref{fig:simulink_system_generator} shows this entire design approach in a block diagram.
The abbreviation ISE stands for Integrated Software Environment, and is Xilinx' development environment that includes the FPGA synthesis tool.

\includepicture [0.8] [0] {Overview of the capabilities of the Simulink System Generator \cite[Abbildung 5.11]{GesslerRalf2014EES}.} {simulink_system_generator} {img/simulink_system_generator}

@@

\includepicture [0.5] [0] [H] {Abstraction levels of the different implementation languages \cite[Abbildung 5.1]{GesslerRalf2014EES}.} {fpga_design_levels} {img/fpga_design_levels}

>>>>

Two commonly used languages therefor are VHDL and Verilog.
Both have similar features to describe hardware in the signal level, with parallel structures and timing-dependent architectures.
The languages can describe a design in a hierarchical order, so that the separate modules can be constructed in a way that an overview of the functionality of the system remains given.
Synthesis, as well as simulation is supported, which allows efficient development of RTL designs.

@@

Fig. \ref{fig:simulink_system_generator} shows this entire design approach in a block diagram.
The abbreviation ISE stands for Integrated Software Environment, and is Xilinx' development environment that includes the FPGA synthesis tool.
ModelSim is a HDL simulator software, that is developed by Mentor Graphics.

\includepicture [0.9] [0] {Capabilities of the Simulink System Generator \cite[Abbildung 5.11]{GesslerRalf2014EES}.} {simulink_system_generator} {img/draw.io/simulink_system_generator}

@@

\includepicture [0.65] [0] [H] {Abstraction levels of the implementation methods \cite[Abbildung 5.1]{GesslerRalf2014EES}.} {fpga_design_levels} {img/draw.io/fpga_design_levels}

%TODO: try to get this figure up into the last page...
